taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-10-11 paper/manuscript.Rmd
Add descriptions to the provider table.

```{r echo = FALSE, results = "asis"}
tibble(provider = c("Integrated Taxonomic Information System, @itis",
                                 "National Center for Biological Information's Taxonomy database, @ncbi",
                                 "Catalogue of Life, @col",
                                 "Global Biodiversity Information Facility Taxonomic Backbone, @gbif",
                                 "FishBase, @fishbase",
                                 #"SeaLifeBase",
                                 "Wikidata, @jorrit", "Open Tree Taxonomy, @Rees2017",
                                 "International Union for Conservation of Nature and Natural Resources, @iucn"),
                    abbreviation = c("itis", "ncbi", "col", "gbif", "fb", #"slb",
                                     "wd", "ott", "iucn"),
                    total_identifiers = map(abbreviation, 
                                            ~taxa_tbl(.x) %>% 
                                              select(acceptedNameUsageID) %>% pull() %>% n_distinct())
) %>% knitr::kable(format = "markdown")

>>>>

```{r echo = FALSE, results = "asis"}
#provider descriptions
desc <- c(itis = "originally formed to standardize taxonomic name usage across many agencies in the United States federal government", 
          ncbi = "",
          col = "", 
          gbif = "", 
          fb = "", 
          wd = "",
          ott = "",
          iucn = "")

tibble(provider = c("Integrated Taxonomic Information System, @itis",
                                 "National Center for Biological Information's Taxonomy database, @ncbi",
                                 "Catalogue of Life, @col",
                                 "Global Biodiversity Information Facility Taxonomic Backbone, @gbif",
                                 "FishBase, @fishbase",
                                 #"SeaLifeBase",
                                 "Wikidata, @jorrit", "Open Tree Taxonomy, @Rees2017",
                                 "International Union for Conservation of Nature and Natural Resources, @iucn"),
                    abbreviation = c("itis", "ncbi", "col", "gbif", "fb", #"slb",
                                     "wd", "ott", "iucn"),
                    total_identifiers = map(abbreviation, 
                                            ~taxa_tbl(.x) %>% 
                                              select(acceptedNameUsageID) %>% pull() %>% n_distinct()),
                    description = desc
) %>% knitr::kable(format = "markdown")
